---
title: "How to deploy the files into Rstudio shiny server"
author: "Bingfang Xu"
date: "Friday, February 26, 2016"
output: pdf_document
---

I have some hard time to deploy the files into Rstudio shiny server. This file is to help myself to do same task in future

## install Rtools from https://cran.r-project.org/bin/windows/Rtools/
## install curl packages
## sudo apt-get install r-cran-xml
## sudo apt-get install libcurl4-gnutis-dev
## install devtools and rconnect

```{r}
install.packages("devtools")

library(devtools)

devtools::install_github('rstudio/rsconnect')

library(rsconnect)
```

## set up an account in shinyApp (https://www.shinyapps.io/)
## request token and authorize the connection.
```{r, echo=FALSE}
rsconnect::setAccountInfo(name='bing-fang24', token='44A36A9C95FF829C74D705FC0753C89E', secret='tu3q5hWU43DWlposSfLMi/7ikbXRUykaA8ZRnE0R')
```
## deploy the files form my locale directory to online server
```{r, echo=FALSE}
rsconnect::deployApp('C:\Users\Bingfang\Desktop\datarep')
```{r, echo=FALSE}